% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\textbf{1. INTRODUCTION}

The given dataset has 1000 SNPs from 50 patients in the case cohort and
100 people in the control cohort and 5 columns representing the name of
the SNP, number of C-alleles in the case cohort, number of T-alleles in
the case cohort, number of C-alleles in the control cohort, and number
of T-alleles in the control cohort.

\textbf{1.1 Generating Your Own Unique Data}

I have used the \emph{\textbf{python3 datasetGenerator.py -\/-ID
1002104402}} to generate the dataset.

\textbf{1.2 Fisher's Exact Test}

I have taken the null hypothesis as ``SNP is not significant''. I had
found out that the number of significant SNPs by checking whether the
p-value of the SNP is less than the effective p-value (5×10−8). I
performed the Fisher\textquotesingle s exact test on C-allele and
T-allele to find out the number of significant SNPs. If it is less, we
conclude the SNP is significant. The number of significant SNPs in our
dataset were \textbf{166}.

The alternative argument for the \emph{fisher\_exact} function is chosen
as ``greater'' as it is the odds ratio of allele C which is higher than
1, allele C is one among the causes of the complex of the genetic trait.

\textbf{1.3 Corrected P-Values}

Before this I had taken the first p-values and checked for significance
of the SNP. Then it taken the Bonferroni-corrected (\emph{α/n})p-value.
Bonferroni-corrected p-value is the original p-value divided by the
number of comparison of the SNP's of 1000. Therefore, the corrected
p-value is 5 × 10 −11. The number of SNPs that are significant under the
corrected p-value is \textbf{114}.

\textbf{1.4 Manhattan Plot}

The Manhattan Plot prompts the scattering of the p-values of all the
SNPs in the dataset. I have also illustrated the threshold of the first
p-value and corrected p-values. While seeing that the major p value
beneath the threshold value. Even the few p-values are in between the
first p-value threshold and the corrected one. The point which are above
the threshold are the ones where the null hypothesis is rejected.

\textbf{2. DIFFICULTY ADJUSTMENT}


The Level and Complexity of the assignment is a bit tough as I worked on
this assignment for 20+ hours, but it was interesting working on various
topics like n no of datasets, fisher exact test, finding p value,
manhattan plotting etc.


\end{document}
